RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective

### 2022-11-28 main.tex
:mag: Update notations

	\emph{Notations:}
	Italic, bold lower-case, and bold upper-case letters denote scalars, vectors and matrices, respectively.
	$\boldsymbol{0}$ and $\boldsymbol{1}$ denote zero and one array of appropriate size, respectively. $\mathbb{I}^{x \times y}$, $\mathbb{R}_+^{x \times y}$, and $\mathbb{C}^{x \times y}$ denote the real unit, real nonnegative, and complex spaces of dimension $x \times y$, respectively.
	$j$ denotes the imaginary unit.
	$\mathrm{diag}(\cdot)$ returns a square matrix with the input vector on its main diagonal and zeros elsewhere.
	$\mathrm{card}(\cdot)$ returns the cardinality of a set.
	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
	$(\cdot)^{(r)}$ and $(\cdot)^{\star}$ denote the $r$-th iterated and terminal solutions, respectively.
	The distribution of a \gls{cscg} random variable with zero mean and variance $\sigma^2$ is denoted by $\mathcal{CN}(0,\sigma^2)$, and $\sim$ means ``distributed as''.
\end{section}

@@

\begin{section}{RIScatter}
	\begin{subsection}{Concepts}
		As a generalization of \gls{bc} and \gls{ris}, RIScatter is a passive scatter protocol that coexists with an active primary system in a flexible and mutualistic manner.
		RIScatter nodes leverage \gls{csi}- and \gls{qos}-based input distribution design to smoothly transition between backscatter modulation and passive beamforming.
		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive backscatter tags.
		The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig. \ref{fg:riscatter_node}, while the input distribution and time structure comparison of scattering applications are shown in Fig. \ref{fg:scatter_comparison}.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fg:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fg:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fg:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.
			}
			\label{fg:riscatter_node}
		\end{figure*}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Time Structure]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Input distribution and time structure of \gls{bc}, \gls{ris}, and RIScatter.
				``PB'' means primary block and ``BB'' means backscatter block.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
		Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms conventional line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
		Besides, joint encoding over multiple co-located RIScatter nodes can further boost the total backscatter rate.
		Relevant \gls{csi} can be acquired by existing low-power estimation techniques.
		For dispersed RIScatter nodes, the cascaded transmitter-node-receiver channels can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
		For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.

@@

		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\mathrm{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.

@@

				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k \label{eq:equivalent_channel_bc}                    \\
				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}}, \label{eq:equivalent_channel_ris}

@@

		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.

@@

			y[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],

@@

			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2

@@

		For the ease of notations, we map the state index tuple $m_{\mathcal{K}}$ to the corresponding index $l \in \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, where $\sigma_1^2,\ldots,\sigma_L^2$ is an ascending sequence.
		Both notations are used interchangeably in the following context.
		As such, the decision region of backscatter symbol tuple $l$ can be written as
		\begin{equation}
			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad 0 \le t_{l-1} \le t_l,
		\end{equation}
		where $t_l$ is the energy decision threshold between hypotheses $\mathcal{H}_{l}$ and $\mathcal{H}_{l+1}$.
		For a given decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^T \in \mathbb{R}_+^{(L+1)}$, we can formulate a \gls{dmtmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ given by
		\begin{equation}
			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \, d z,
			\label{eq:dmtmac}
		\end{equation}
		over which adaptive input distribution design and backscatter channel coding can be performed.
		\label{st:system_model}
	\end{subsection}

	\begin{subsection}{Achievable Rates}
		Let $P_k(x_{m_k})$ be the input probability of node $k$ at state $m_k$, and $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{I}^{M}$ be the input distribution vector.
		% Denote the input probability of node $k$ at state $m_k$ as $P_k(x_{m_k})$, and the input distribution vector as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{I}^{M}$.
		For dispersed nodes with independent encoding, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
		\begin{equation}
			P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k}).
			\label{eq:equivalent_distribution}
		\end{equation}
		Following \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple variable $\hat{x}_{\mathcal{K}}$ as
		\begin{equation}
			I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'})},
			\label{eq:backscatter_information_function}
		\end{equation}
		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$ is the probability of output tuple $\hat{x}_{m_{\mathcal{K}}'}$.
		We also define the backscatter marginal information of letter $x_{m_k}$ as
		\begin{equation}
			I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			\label{eq:backscatter_marginal_information}
		\end{equation}
		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
		Hence, the backscatter mutual information can be written as
		\begin{equation}
			I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
			\label{eq:backscatter_mutual_information}
		\end{equation}

		Once node messages are successfully decoded, we can re-encode for exact backscatter symbol tuple $x_{\mathcal{K}}$, recover their reflection patterns by \eqref{eq:backscatter_modulation}, and retrieve the primary equivalent channel by \eqref{eq:equivalent_channel}.
		Therefore, the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
		\begin{equation}
			I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
			\label{eq:primary_information_function}
		\end{equation}
		the primary marginal information of letter $x_{m_k}$ is
		% the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
		\begin{equation}
			I_{\mathrm{P},k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}),
			\label{eq:primary_marginal_information}
		\end{equation}
		and the average primary mutual information is
		\begin{equation}
			I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}).
			\label{eq:primary_mutual_information}
		\end{equation}

		With a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information as
		\begin{align}
			I(x_{m_{\mathcal{K}}})
			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
			I_k(x_{m_k})
			 & \triangleq \rho I_{\mathrm{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
			I(x_{\mathcal{K}})
			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
		\end{align}
		where $\rho \in \mathbb{I}$ is the \gls{qos} of the primary link.
		We notice the average primary rate \eqref{eq:primary_mutual_information} depends on the input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmtmac} \eqref{eq:dmtmac} that relates to active beamforming and decision thresholds.
		\label{st:information_theory}
	\end{subsection}
	\label{st:riscatter}
\end{section}

\begin{section}{Rate-Region Characterization}
	To characterize the achievable primary-(total-)backscatter rate region for the RIScatter system in Fig. \ref{fg:riscatter_network}, we aim to maximize the weighted sum rate with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ by
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		\addConstraint{\boldsymbol{1}^T \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
		\addConstraint{\boldsymbol{p}_k}{\ge \boldsymbol{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:nonnegative_threshold}}
	\end{maxi!}

@@

			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\boldsymbol{h}_{\mathrm{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} g_{m_{\mathcal{K}}}(t_{l-1},t_l),

@@

				\Require $Q$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\varepsilon$

@@

				\State Set $\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}

@@

				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k\Bigr) \boldsymbol{w} + v[n],

>>>>

	\emph{Notations:}
	Italic, bold lower-case, and bold upper-case letters denote scalars, vectors and matrices, respectively.
	$\boldsymbol{0}$ and $\boldsymbol{1}$ denote zero and one array of appropriate size, respectively. $\mathbb{I}^{x \times y}$, $\mathbb{R}_+^{x \times y}$, and $\mathbb{C}^{x \times y}$ denote the real unit, real nonnegative, and complex spaces of dimension $x \times y$, respectively.
	$j$ denotes the imaginary unit.
	$\mathrm{diag}(\cdot)$ returns a square matrix with the input vector on its main diagonal and zeros elsewhere.
	$\mathrm{card}(\cdot)$ returns the cardinality of a set.
	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
	$(\cdot)^{(r)}$ and $(\cdot)^{\star}$ denote the $r$-th iterated and terminal solutions, respectively.
	The distribution of a \gls{cscg} random variable with zero mean and variance $\sigma^2$ is denoted by $\mathcal{CN}(0,\sigma^2)$, and $\sim$ means ``distributed as''.
\end{section}

@@

\begin{section}{RIScatter}
	\begin{subsection}{Concepts}
		As a generalization of \gls{bc} and \gls{ris}, RIScatter is a passive scatter protocol that coexists with an active primary system in a flexible and mutualistic manner.
		RIScatter nodes leverage \gls{csi}- and \gls{qos}-based input distribution design to smoothly transition between backscatter modulation and passive beamforming.
		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive backscatter tags.
		The block diagram, equivalent circuit, and scatter model of a RIScatter node are illustrated in Fig. \ref{fg:riscatter_node}, while the input distribution and time structure comparison of scattering applications are shown in Fig. \ref{fg:scatter_comparison}.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fg:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fg:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fg:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
			}
			\label{fg:riscatter_node}
		\end{figure*}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Time Structure]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Input distribution and time structure of \gls{bc}, \gls{ris}, and RIScatter.
				``PB'' means primary block and ``BB'' means backscatter block.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node semi-randomly chooses the reflection state for each backscatter block with the guidance of input probability distribution $P(\Gamma_m)$ at state $m$.
		Such an adaptive backscatter coding boils down to degenerate distribution of \gls{ris} when primary link is prioritized, and outperforms conventional line coding with equiprobable inputs (e.g., FM0 for \gls{rfid}) when backscatter link is prioritized.
		Besides, joint encoding over multiple co-located RIScatter nodes can further boost the total backscatter rate.
		Relevant \gls{csi} can be acquired by existing low-power estimation techniques.
		For dispersed RIScatter nodes, the cascaded transmitter-node-receiver channels can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
		For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.

@@

		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.

@@

				\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
				 & = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}}, \label{eq:equivalent_channel_ris}

@@

		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.

@@

			y[n] = \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],

@@

			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2

@@

		For the ease of notations, we map the state index tuple $m_{\mathcal{K}}$ to the corresponding index $l \in \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, where $\sigma_1^2,\ldots,\sigma_L^2$ is an ascending sequence.
		Both notations are used interchangeably in the following context.
		As such, the decision region of backscatter symbol tuple $l$ can be written as
		\begin{equation}
			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad 0 \le t_{l-1} \le t_l,
		\end{equation}
		where $t_l$ is the energy decision threshold between hypotheses $\mathcal{H}_{l}$ and $\mathcal{H}_{l+1}$.
		For a given decision threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{(L+1)}$, we can formulate a \gls{dmtmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ given by
		\begin{equation}
			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \, d z,
			\label{eq:dmtmac}
		\end{equation}
		over which adaptive input distribution design and backscatter channel coding can be performed.
		\label{st:system_model}
	\end{subsection}

	\begin{subsection}{Achievable Rates}
		Let $P_k(x_{m_k})$ be the input probability of node $k$ at state $m_k$, and $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$ be the input distribution vector.
		% Denote the input probability of node $k$ at state $m_k$ as $P_k(x_{m_k})$, and the input distribution vector as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^\mathsf{T} \in \mathbb{I}^{M}$.
		For dispersed nodes with independent encoding, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
		\begin{equation}
			P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k}).
			\label{eq:equivalent_distribution}
		\end{equation}
		Following \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple variable $\hat{x}_{\mathcal{K}}$ as
		\begin{equation}
			I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'})},
			\label{eq:backscatter_information_function}
		\end{equation}
		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$ is the probability of output tuple $\hat{x}_{m_{\mathcal{K}}'}$.
		We also define the backscatter marginal information of letter $x_{m_k}$ as
		\begin{equation}
			I_{\text{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			\label{eq:backscatter_marginal_information}
		\end{equation}
		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
		Hence, the backscatter mutual information can be written as
		\begin{equation}
			I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
			\label{eq:backscatter_mutual_information}
		\end{equation}

		Once node messages are successfully decoded, we can re-encode for exact backscatter symbol tuple $x_{\mathcal{K}}$, recover their reflection patterns by \eqref{eq:backscatter_modulation}, and retrieve the primary equivalent channel by \eqref{eq:equivalent_channel}.
		Therefore, the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
		\begin{equation}
			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
			\label{eq:primary_information_function}
		\end{equation}
		the primary marginal information of letter $x_{m_k}$ is
		% the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
		\begin{equation}
			I_{\text{P},k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}),
			\label{eq:primary_marginal_information}
		\end{equation}
		and the average primary mutual information is
		\begin{equation}
			I_{\text{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}).
			\label{eq:primary_mutual_information}
		\end{equation}

		With a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information as
		\begin{align}
			I(x_{m_{\mathcal{K}}})
			 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
			I_k(x_{m_k})
			 & \triangleq \rho I_{\text{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\text{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
			I(x_{\mathcal{K}})
			 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
		\end{align}
		where $\rho \in \mathbb{I}$ is the \gls{qos} of the primary link.
		We notice the average primary rate \eqref{eq:primary_mutual_information} depends on the input distribution and active beamforming, while the total backscatter rate depends on the input distribution and \gls{dmtmac} \eqref{eq:dmtmac} that relates to active beamforming and decision thresholds.
		\label{st:information_theory}
	\end{subsection}
	\label{st:riscatter}
\end{section}

\begin{section}{Rate-Region Characterization}
	To characterize the achievable primary-(total-)backscatter rate region for the RIScatter system in Fig. \ref{fg:riscatter_network}, we aim to maximize the weighted sum rate with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ by
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		\addConstraint{\boldsymbol{1}^\mathsf{T} \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
		\addConstraint{\boldsymbol{p}_k}{\ge \boldsymbol{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:nonnegative_threshold}}
	\end{maxi!}

@@

			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\boldsymbol{h}_{\text{E}}(x_{m_{\mathcal{K}}})\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} g_{m_{\mathcal{K}}}(t_{l-1},t_l),

@@

				\Require $Q$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\varepsilon$

@@

				\State Set $\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}

@@

				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k\Bigr) \boldsymbol{w} + v[n],
